---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggtwotone

<!-- badges: start -->

<!-- badges: end -->

`ggtwotone` is an R package that extends `ggplot2` with dual-stroke and
contrast-aware geoms. It helps you create clear, high-contrast
annotations and lines that remain visible across complex or variable
backgrounds.

## What's Inside

-   geom_segment_dual() Dual-stroke line segments with vertical offset

-   geom_lm_dual() Dual-tone regression line with contrast-aware strokes

-   geom_curve_dual() Dual-stroke curved line annotations

-   geom_curve_dual_function() Plot mathematical or statistical
    functions as smooth dual-stroke curves

-   geom_text_contrast() Automatically switches between light/dark text
    color based on background

-   adjust_contrast_pair() Helper function to find contrast-boosted
    color pairs using WCAG/APCA

## Installation

You can install the development version of ggtwotone from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("bwanniarachchige2/ggtwotone")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggplot2)
library(ggtwotone)

df <- data.frame(x = 1:3, y = 1, xend = 1:3, yend = 2)

ggplot(df) +
  geom_segment_dual(
    aes(x = x, y = y, xend = xend, yend = yend),
    color1 = "#FFFFFF", color2 = "#000000", linewidth = 2
  ) +
  theme_dark()
```

```{r}
ggplot() +
  geom_curve_dual_function(
    fun = dnorm,
    xlim = c(-3, 3),
    color1 = "#EEEEEE", color2 = "#222222",
    offset = 0.004,
    linewidth = 1.2,
    smooth = TRUE
  ) +
  theme_dark()

```

# Motivation

In real-world plots, especially on mixed backgrounds (grayscale tiles,
images, or map layers), default ggplot2 annotations can disappear.
ggtwotone solves this with:

-   Dual-stroke visibility: top and bottom layers ensure readability

-   Contrast checking: uses APCA/WCAG to optimize color pairing

-   Fallback safety: gracefully assigns black/white when needed

You can explore all functions in the
[Reference](https://bwanniarachchige2.github.io/ggtwotone/) Manual, or
see them in the R help tab after loading the package.
